### 2025-01-23 acronyms/acronyms.tex
acronyms

\newacronym{cic}{CISAC}{Center for Interantional Security and Cooperation}

@@

>>>>

\newacronym{cic}{CISAC}{Center for International Security and Cooperation}

@@

\newacronym{saf}{SAFSTOR}{Safe Storage}
\newacronym{dec}{DECON}{Decontamination \& Dismantlement}
\newacronym{mse}{MSRE}{Molten Salt Reactor Experiment}
\newacronym{psd}{PSDAR}{Post Shutdown Decommissioning Activities Report}
\newacronym{ap}{AP}{Activation Product}
\newacronym{hdap}{HDAP}{High-Dose Activation Product}
\newacronym{gtcc}{GTCC}{Greater than Class C}
\newacronym{isfsf}{ISFSF}{Interim Spent Fuel Storage Facility}
